\chapter{Using \dtypkgu{}}

	\section{The Interface Window}%WX%3||||
	The elements of the \IXarg{interface} presented by \IXpkg{}
	are arranged in a manner that has been typical in
	windowing systems for many years, and will probably
	seem familiar to most users. Most elements are common,
	but a few are specific to \IXpkg{}. A few are similar
	to common elements in most windowed applications,
	but with some differences in behavior.

	The main groups of \IXarg{interface} elements are
	discussed briefly, from the top down in order of appearance,
	in the following subsections.
		\subsection{The Menu Bar}%WX%4||||
		The \IXarg{menu} ``bar'' consists of the labels, arranged
		horizontally, nearest the top of the window. Each
		label can be selected with the \IXarg{mouse} and
		will produce a small rectangular window, the
		\IXnewterm{menu}, with selectable labels, or
		\emph{items}.
		
		Selecting a \IXarg{menu} item invokes an action
		such as saving or closing data. When an item does not
		make sense for the current state of the data, it
		cannot be selected, and this is indicated by showing the
		label ``greyed,'' or dimmed, in appearance.
		
		Many of the \IXarg{menu} labels have additional text
		near the right-side edge, such as ``Ctrl+S.''  These
		indicate combinations of keys that will invoke the
		action associated with the \IXarg{menu} item without
		selecting the \IXarg{menu} with the mouse.
			\subsubsection{The File Menu}%xxxWX%5||501000||
			This \IXarg{menu} provides items that generally
			apply to the current data, or ``file.''
				\begin{table}[htbp]
				\centering
				\textsf{
				\begin{tabular}[c]{ | l | l || p{5.33cm} | }
				\hline
				\textsc{Item}: & \textsc{Keys}: & \textsc{Action}:\\ \hline
				\hline \hline
				Save & Ctrl+S & save data with current name\\ \hline
				Save As & --- & save data with a new name\\ \hline
				New & Ctrl+N & create a tab for new data\\ \hline
				Open Here & --- & open (load) file data in current tab\\ \hline
				Open & Ctrl+O & open (load) file data in a new tab\\ \hline
				Close & Ctrl+W & close the data (file), leave tab\\ \hline
				Close Tab & --- & close the data (file), close tab\\ \hline
				Export & Ctrl+E & save the data as \IXpov{} \IXarg{SDL}\\ \hline
				Export As & --- & save as \IXarg{SDL} with a new name\\ \hline
				\hline
				Quit & Ctrl+Q & quit the \textrm{\dtythispkgname{}} program\\
				\hline
				\end{tabular}
				}%\textsf
				\caption{The Items of the File Menu}
				\label{tab:File_menu}
				\end{table}
			
		\subsection{The Tool Bar}%WX%4||||
		The \IXnewterm{tool} bar is similar to the \IXarg{menu}
		bar.
		\subsection{The Editing Area}%WX%4||||
		\subsection{The Status Bar}%WX%4||||

	\section{Creating and Editing}%WX%3||||

	\section{Tips}%WX%3||||


%\IXpkgu{} is an interactive program with a
%graphical interface. Interaction is primarily by use of a mouse
%(or any pointing device from which the windowing system delivers
%`mouse' events to software).
%\subsection{Overview}%WX%4||403000||
%\subsection{Mouse and Key}%WX%4||404000||
%% no coded comment for subsubsection
%\subsubsection{Operations}%xxxWX%5||501000||
%\subsection{Usage Table}%WX%4||405000||
%
